---
Title:"My Rmd document"
author:"Sreeja Vishaly"
date:"`r format(Sys.time(),'%d %B, %Y')`"
bibliography: example.bib
output:bookdown::html_document-2
---
```
We are using the Starwars dataset, which has `r dim(starwars)[1]` and `r dim(starwars)[2]` columns.

```{r, starwars-plot, fig.cap= "A ggplot of starwars data"}

library(tidyverse)

starwars%>%
 filter(species=="Human") %>%
ggplot() +  
 aes(x=height,
     y= mass)+
  geom_point()
```
Starwars Visualization \@ref(fig:starwars-plot)...


```{r, starwars-tbl}
library(tidyverse)
starwars%>%
 filter(species=="Human") %>%
 select(name,
        height,
        mass,
        homeworld) %>%
knitr::kable(caption = "A knitr kable table of starwars data")
```

Starwars data in Table \@ref(tab::starwars-tbl)...


```{r, my-fig, fig.cap="My non-code figure"}

knitr::include_graphics("https://wall.alphacoders.com/big.php?i=792609")

```

The picture of Legend \@ref(fig:myfigure)...


---

Title:"My great report"
bibiliography:"Sreeja Vishaly"
date:"`r format(Sys.time(),'%d %B, %Y')`"
output:bookdown::html_document-2

---

Let's also see check out the article "Terminologies for reproducible research". [@barba2018terminologies].

# References cited